%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother


% what is your name?
\newcommand{\myname}{Arnau Quera-Bofarull}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {\myname},
    pdfkeywords = {},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \nobibliography{papers}
    \bibliographystyle{unsrt}

    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Institute for Computational Cosmology\\
        Department of Physics \\
        Durham University
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:arnau.quera-bofarull@durham.ac.uk}{arnau.quera-bofarull@durham.ac.uk}\\
        +44 7736996791\\
        \href{www.arnau.space}{www.arnau.space}
    \end{minipage}


    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Astrophysics and Data Science, Durham University, UK (Expected 2022)
        \item[M.S.]  \tab{}Physics, Heidelberg University, Germany, 2017
        \item[B.S.]  \tab{}Physics, University of Barcelona, Spain, 2015
        \item[B.S.]  \tab{}Mathematics, University of Barcelona, Spain, 2015

    \end{tablist}

    \section*{Research Experience}

    \begin{tablist}

        \item[2017--]   \tab{}Institute for Computational Cosmology,  Durham University, UK\\
                                Development of HPC code to calculate black hole outflows.
        \item[2020--]   \tab{}United Nations Global Pulse, USA\\
                                Modelling the spread of Covid-19 in refugee camps with agent-based simulations.
        \item[2020--]   \tab{}Institute for Data Science, Durham University, UK\\
                                Main developer of the \textsc{June} codebase, an agent-based model to simulate the spread of Covid-19 with fine grained population data. 
        \item[2019]   \tab{}Centre for Computational Sciences, Tsukuba University, Japan\\
                                Modelling of Active Galactic Nuclei accretion discs with HPC simulations.
        \item[2019]   \tab{}Centre for Research on Education and Social Justice, York University, UK\\
                                Application of Machine Learning algorithms to predicting progression to postgraduate studies in England.
        \item[2019]   \tab{}Boeing Digital Aviation \& Analytics, Germany\\
                                Computer vision for process tracking in aircraft ground operations.
        \item[2018]   \tab{}Ibex Innovations, UK\\
                                Computer vision for X-ray medical image segmentation.
                                
    \end{tablist}


    %\section*{Appointments}

    %\begin{tablist}

    %    \item[2019--]   \tab{}University of Southern California \\
    %                         Assistant Professor, Department of Urban Planning and Spatial Analysis, 2019-- \\
    %                         Affiliate Faculty, Spatial Sciences Institute, 2021--

    %    \item[2018--19] \tab{}Northeastern University \\
    %                         Assistant Professor, School of Public Policy and Urban Affairs \\
    %                         Affiliate Faculty, Network Science Institute \\
    %                         Affiliate Faculty, Global Resilience Institute

    %    \item[2017--18] \tab{}University of California, Berkeley \\
    %                         Postdoctoral Researcher, Department of City and Regional Planning

    %\end{tablist}



    %\section*{Research Areas}

    %\begin{itemize}

    %    \item Urban informatics and geospatial data science: computational statistics, visualization, and spatial analysis
    %    \item Transportation planning: street network design, access, equity, and urban form
    %    \item Housing: emerging technology platforms' impacts on markets, residential mobility, and segregation

    %\end{itemize}



    \section*{Publications}

    \subsection*{Journal Articles}

    \begin{tablist}

        \item[2021] \tab{}\bibentry{cuesta-lazaro_vaccinations_2021}

        \item[2021] \tab{}\bibentry{bullock_operational_2021}

        \item[2020] \tab{}\bibentry{aylett-bullock_june_nodate}

        \item[2020] \tab{}\bibentry{quera-bofarull_qwind_2020}

        \item[2018] \tab{}\bibentry{cuesta-lazaro_gravitational_2018}

    \end{tablist}


    \subsection*{Conference Proceedings}

    \begin{tablist}

        \item[2019] \tab{}\bibentry{bullock_xnet_2019}

    \end{tablist}


    \section*{Invited Talks}

    \begin{tablist}

    \item[2020] \tab{}\enquote{\textsc{JUNE}: Modelling the spread of Covid-19 in England}. Public Health England modelling group, Cambridge, UK. Jul 3.

    \item[2020] \tab{}\enquote{Simulating UV line-driven winds in AGNs.} Hokkaido University, Japan. Feb 5.

    \item[2019] \tab{}\enquote{Computer vision for X-ray medical image segmentation.} Rutherford Appleton Laboratory, UK, Mar 5.


    \end{tablist}

    \subsection*{Campus Talks}

    \begin{tablist}

        \item[2021] \tab{}\enquote{10 reason why I use (and love) Julia} Institute for Computational Cosmology, Durham, UK, Mar 29.

        \item[2019] \tab{}\enquote{Deep Learning and graph networks} Institute for Data Science, Durham, UK, Oct. 17

        \item[2018] \tab{}\enquote{Simulating AGN feedback.} Institute for Computational Cosmology, Durham, UK, Dec 18.

    \end{tablist}


    \section*{Conference Activity}

    \subsection*{Talks}

    \begin{tablist}

        \item[2021] \tab{}\enquote{UV line-driven winds: Dependence on black hole properties.} Black hole accretion disc winds. Durham, UK.\@ Sep 6--9.

        \item[2019] \tab{}\enquote{Computer vision for X-ray medical image segmentation.} Beyond the Lab. Edinburgh, UK.\@ Jan 24.

    \end{tablist}

    \subsection*{Poster presentations}

    \begin{tablist}

        \item[2019] \tab{}\enquote{UV line-driven winds}. Feedback and its role in galaxy formation. Spetses, Greece. June 25--29.

    \end{tablist}

    \subsection*{Sessions Organized}

    \begin{tablist}

        \item[2021] \tab{}STFC Data Intensive Science Summer School 2021. Durham, UK. Sep 13--17.

    \end{tablist}



    \section*{Grants and Awards}

    \subsection*{Awards and Honors}

    \begin{tablist}

        \item[2021] \tab{}RAMP Early Career Investigator Award (RECIA), Royal Society
        \item[2020] \tab{}Department of Physics Award for Excellence 2020, Durham University
        \item[2019] \tab{}No-Bull award (Carmen Optimization Workshop), Boeing

    \end{tablist}

    \subsection*{Grants and Fellowships}

    \begin{tablist}

        \item[2019] \tab{}JSPS Short Term Pre/Postdoctoral Fellowship (\pounds 6,500).
        \item[2017-] \tab{}STFC CDT Scholarship

    \end{tablist}

    \section*{Teaching}

    \subsection*{Durham University}

    \begin{itemize}

        \item Planets and Cosmology (2017,2018,2020)
        \item Version control with Git (2020, 2021)

    \end{itemize}

    \section*{Outreach}

    \begin{tablist}

        \item[2019] \tab{}\enquote{Changing Cosmic Percetions}. Durham, UK.
        \item[2018,19] \tab{}\enquote{Celebrate Science}. Durham, UK.
        \item[2018] \tab{}\enquote{From Atoms to Galaxies}. Durham, UK.

    \end{tablist}

    \section*{Languages}

    \begin{tablist}

    \item Catalan (Native)
    \item English (Fluent)
    \item German (Intermediate)
    \item Japanese (Elementary)
    \item Spanish (Native)

    \end{tablist}




    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
